This complexity of the recursion process mainly depends on the additions.
Let's define $F_{i, j}$ as when such recursion process start at calculating $\binom{i}{j}$,
the number of additions it will do.

obviously, $F_{i, j}$ consists of three parts below:
\begin{itemize}
\item $F_{i - 1, j - 1}$: add the number of addition operations in $\binom{i - 1}{j - 1}$ to the current answer.
\item $F_{i - 1, j}$: add the $\binom{i - 1}{j - 1}$'s answer.
\item $1$: the number of additions which used to add $\binom{i - 1}{j - 1}$ and $\binom{i - 1}{j}$ up.
\end{itemize}

Thus we have
\begin{equation}\label{equation3}
F_{i, j} = F_{i - 1, j - 1} + F_{i - 1, j} + 1
\end{equation}
This is a quite strange and Pascal-like equation.
Consider
\[(F_{i, j} + 1) = (F_{i - 1, j - 1} + 1) + (F_{i-1, j} + 1)\]
We can easily find out that
\[F_{i, j} + 1 = \binom{i}{j} + \binom{i}{j-1} + \binom{i}{j+1}\]
Therefore
\begin{equation}\label{equation4}
F_{i, j} = \binom{i}{j} + \binom{i}{j-1} + \binom{i}{j+1} - 1
\end{equation}
Hence, the total number of addition operation is
\[\binom{n}{k} + \binom{n}{k-1} + \binom{n}{k+1} - 1\]

The lower bound of the complexity of adding two numbers together being $O(1)$ and the upper bound can be $O(\log\binom{n}{k})$,
we can easily figure out that the lower bound of the complexity of this algorithm is
\[O\left(\binom{n}{k} + \binom{n}{k-1} + \binom{n}{k+1}\right) = O\left(\binom{n}{k}\right)\]
While the upper bound is
\[O\left(\binom{n}{k}\log \binom{n}{k}\right)\]

When $n = 50, k = 25$, this algorithm needs to do about $1.3 \times 10^{16}$ additions, which is too slow. As the complexity of reading input data is only $O(\log n)$, which is much smaller than the complexity of calculating $\binom{n}{k}$, Hence this algorithm is inefficient.
