Consider constructing this special sequence by Recursive Process. Let $n = 2^d$, We define $F(d)$ is a process which can give us a acceptable sequence which length is $2^d$. when $d$ equals to zero seems trivial, just return the only one element. when $d > 0$, consider making the number of comparisons as much as possible, after sorting this sequence, we split the sequences in two parts. choose the index of 1, 3, 5, .. $2^d-1$ into one part, while the index of 2, 4, 6 .. $2^d$ into another part. then put these two parts into $F(d - 1)$ individually. After that, merge these two new parts(one part is first, then another part), thus we get the sequence which $F(d)$ need.

Now, we prove the total comparison of sequence which $F(d)$ provides is $n\log n - n + 1$, consider prove by induction.

\item Proof by introduction
\begin{proof}
the total comparison of sequence which $F(d)$ provides is $n\log n - n + 1$.
\begin{enumerate}
    \item Basic step\\
    When $d = 0, n = 1$, it's clearly right because:
	\[n\log n - n + 1 = 0\]

    while the only element don't need to compare.
    \item Induction step\\
    Assume that the comparisons fit when $F(d - 1)$ works, consider $F(d)$.

    Consider the process of merge sort, first it split the sequences into two parts, which are the first half of the sequence and the rest. the two parts are all constructed by $F(d - 1)$, so while doing this, it costs $2 \times (n \log n - n + 1) = 2 \times (2 ^{d-1} \times (d - 1) - 2^{d - 1} + 1)$ comparisons, where $n = 2^{d - 1}$.

    After that, we can easily find that merge these two parts need $2^{d} - 1$ comparisons, because the first parts contains the $1st, 3rd, 5th ..$ large number of the whole sequences, when the other part contains the $2nd, 4th, 6th .. $, so the total comparisons is:
    \[2 \times (2^{d - 1} \times (d - 1) - 2^{d - 1} + 1) + 2^{d} - 1 = 2^{d} \times d - 2^{d} + 1\]

    \item Conclusion\\
	By induction, we have proved that the total comparison of sequence which $F(d)$ provides is $n\log n - n + 1$, where $n = 2^{d}$.
\end{enumerate}
\end{proof}

